Static Analysis by Path Focusing

### 2011-05-11 report/report.tex
report update + added some benchmarks

	To be completed\dots

\begin{tabular}{|c|c|c|c||c|c|} \hline

			& \multicolumn{3}{c||}{Path Focusing} & \multicolumn{2}{c|}{Lookahead
			Widening} \\ \hline
Benchmark	& \multicolumn{2}{c|}{time} & result	& time	& result	\\
\cline{2-3}	& z3 & Yices				& & & \\
\hline

>>>>

	In this section, we evaluate our \emph{Lookahead Widening} and \emph{Path
	Focusing} implementations. We can compare their execution time in some
	practical cases, and the precision of their results. Table \ref{experiments}
	gives the results of the analyzer in various examples, some of them taken
	from the recent literature \cite{CGGMP05,GopanR06}.

	In all experiments, the set $P_R$ is chosen equal to $P_W \cup P_{ret} \cup
	P_{init}$,
	where $P_W$ is the set of widening points. $P_{init}$ is the set of starting
	points of the program, and $P_{ret}$ is the set of points that have no
	successors.

\begin{table}[!h]
\centering \scriptsize
\begin{tabular}{|c|c|c|l||c|l|} \hline

			& \multicolumn{3}{c||}{Path Focusing} & \multicolumn{2}{c|}{Lookahead
			Widening} \\ \cline{2-6}
Benchmark	& \multicolumn{2}{c|}{time} & result	& time	& result	\\
\cline{2-3}	& Z3 & Yices				& & & \\
\hline \hline

Gopan.c & 0.088s & 0.080s & \begin{tabular}{l}
-x.0 - y.0 + 102 >= 0 \\
y.0 >= 0              \\
x.0 - y.0 >= 0        
\end{tabular} & 0.032 & \begin{tabular}{l}
-x.0 - y.0 + 102 >= 0 \\
y.0 >= 0              \\
x.0 - y.0 >= 0        
\end{tabular} \\ \hline

Beyer.c & 0.084s & 0.076s & \begin{tabular}{l}
 -x.0  + 100 >= 0 \\
 y.0 - 50 >= 0    \\
 -x.0 + y.0 >= 0  
\end{tabular} & 0.032 & \begin{tabular}{l}
-x.0  + 100 >= 0 \\
 y.0 - 50 >= 0 \\
-x.0 + y.0 >= 0
\end{tabular} \\ \hline

Boustr.c & 0.100s & 0.088s & \begin{tabular}{l}
 -2x.0 + d.0 + 1999 >= 0 \\
 -2x.0 + 3d.0 + 2001 >= 0 \\
 -d.0 + 1 >= 0
\end{tabular} & 0.064 & \begin{tabular}{l}
 -1996x.0 + 4991d.0 + 1998995 >= 0\\
 -2x.0 + d.0 + 1999 >= 0 \\
 -d.0 + 1 >= 0 \\
\end{tabular} \\ \hline

ex8.cpp & 0.516s & 0.408s & \begin{tabular}{l}
 -y.0 - x.0 + 1 >= 0\\
 -y.0 + x.0 + 1 >= 0\\
 y.0 - x.0 + 1 >= 0\\
 y.0 + x.0 + 1 >= 0
\end{tabular} & 0.208 & \begin{tabular}{l}
-x.0 + 1 >= 0 \\
x.0 + 1 >= 0 
\end{tabular} \\ \hline

ex9.cpp & 0.084s & 0.082s & \begin{tabular}{l}
 r.0 = 0 \\
-i.0 + 100 >= 0 \\
i.0 >= 0
\end{tabular} & 0.052 & \begin{tabular}{l}
-i.0 + 100 >= 0\\
r.0 >= 0 \\
i.0 - r.0 >= 0 \\
24i.0 - 25r.0 + 75 >= 0
\end{tabular} \\ \hline

test1.c & 0.064s & 0.064s & \begin{tabular}{l}
2j.0 + i.0 - 21 = 0 \\
-j.0 + 10 >= 0 \\
j.0 - 6 >= 0
\end{tabular} & 0.016 & \begin{tabular}{l}
2j.0 + i.0 - 21 = 0 \\
-j.0 + 10 >= 0 \\
j.0 - 6 >= 0
\end{tabular} \\ \hline

\end{tabular}
\caption{Results of \emph{Path Focusing} and \emph{Lookahead Widening}
techniques applied to various benchmarks}
\label{experiments}
\end{table}

\emph{Path Focusing} appears to always perform similarly or better than 
\emph{Lookahead Widening}. Indeed, it is more precise in the case of programs
containing control-flow merges inside of loops, because of the distinction
between all the paths of the loop.
